A Test of the Frequency Independence Assumption of Power System Coefficients used in Geomagnetically Induced Current Estimates

### 2019-07-16 paper.tex
Updates from Overleaf

The 1-second-cadence GIC data used span a total of 35 days across 10 intervals that start and end at midnight Japan Standard Time (JST) and are listed in Table~\ref{intervals}. These data along with a map showing the location of the transformer and the connected 187~kV power line have been presented previously in \citet{Watari2009} and \cite{Watari2015}. These time intervals are those for which GIC data was made available with the exception of three days for which there were obvious problems with either the electric field or GIC measurements. The GIC dataset includes 1~s raw data and 1~Hz low-pass-filtered raw measurements. The results presented here are for the 1~Hz low-pass-filtered GIC measurements.

One-second-cadence electric and magnetic field measurements from Memanbetsu Magnetic Observatory (geodetic latitude: 43.910 N, geodetic longitude: 144.189 E) were obtained from the Japan Meteorological Agency data portal.

@@

\acknowledgments
Magnetic and electric field measurements made at the Kakioka Magnetic Observatory was obtained from the Japan Meteorological Agency Data Portal \url{http://www.kakioka-jma.go.jp/obsdata/metadata/en}. We would like to thank the Hokkaido Electric Power Co. for the GIC measurements at the Memanbetsu substation and Shinichi Watari for communicating and preparing the GIC data and providing feedback on the manuscript. We also thank Ikuko Fujii for providing clarifications on the geoelectric instrument response, Trevor Gaunt and Emanuel Benabeau for review and comments on part (1) of Section 5, and E. Josh Rigler for substantial feedback and review.
%\clearpage

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_raw_All_20060805.pdf}
\caption{(Top) Geomagnetic field measured at the Memanbetsu Magnetic Observatory (MMB). (Middle) Geoelectric field measured at the Memanbetsu Magnetic Observatory (MMB), which is $\sim$9 km from the Memanbetsu substation. (Bottom) GIC measurements measured in a grounded neutral point of a Y-connected three-phase transformer connected to a 187 kV bus at the Memanbetsu substation of the Hokkaido Power Co. The subscripts $x$ and $y$ correspond to Geographic North and East, respectively, and the date labels are for Universal Time.}
\label{sample}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/map.pdf}
\caption{Out-of-sample model predictions (top) and predictions errors for a 1-day interval. Note that the scales for the error time series differ from that for the top panel so that the error amplitudes are scaled up by a factor of 2.}
\label{predictions}
\end{figure}

>>>>

The 1-second-cadence GIC data used span a total of 35 days across 10 intervals that start and end at midnight Japan Standard Time (JST) and are listed in Table~\ref{intervals}. These data have been presented previously in \citet{Watari2009} and \cite{Watari2015}. These time intervals are those for which GIC data was made available with the exception of three days for which there were obvious problems with either the electric field or GIC measurements. The GIC dataset includes 1~s raw data and 1~Hz low-pass-filtered raw measurements and the results presented are for the 1~Hz low-pass-filtered GIC measurements.

GIC was measured in a grounded neutral point of a Y-connected three-phase transformer connected to the 187 kV bus at the Memanbetsu substation of the Hokkaido Power Co. The 187 kV line extends from the Ashro to Memanbetsu substation, which are both grounded. Memanbetsu is an end point of the line.

One-second-cadence electric and magnetic field measurements from Memanbetsu Magnetic Observatory (geodetic latitude: 43.910 N, geodetic longitude: 144.189 E) were obtained from the Japan Meteorological Agency data portal. The location of the observatory and substation are shown in Figure~\ref{map}.

@@

\acknowledgments
Magnetic and electric field measurements made at the Kakioka Magnetic Observatory was obtained from the Japan Meteorological Agency Data Portal \url{http://www.kakioka-jma.go.jp/obsdata/metadata/en}. We would like to thank the Hokkaido Electric Power Co. for the GIC measurements at the Memanbetsu substation and Shinichi Watari for communicating and preparing the GIC data and providing feedback on the manuscript. We also thank Ikuko Fujii for providing clarifications on the geoelectric instrument response, Trevor Gaunt and Emanuel Benabeau for review and comments on part (1) of Section 5, and Josh Rigler for substantial feedback and review.
%\clearpage

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/map.pdf}
\caption{Locations of measurement sites for GIC, at the Memanbetsu substation, and the geoelectric and geomagnetic field measurement site at Memambetsu Magnetic Observatory. The distance from the observatory to the substation is $\sim$9 km.}
\label{map}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_raw_All_20060805.pdf}
\caption{(Top) Geomagnetic field measured at the Memanbetsu Magnetic Observatory (MMB). (Middle) Geoelectric field measured at the Memanbetsu Magnetic Observatory (MMB). The subscripts $x$ and $y$ correspond to Geographic North and East, respectively, and the date labels are for Universal Time.}
\label{sample}
\end{figure}
